Syntax and Semantics of Abstract Binding Trees

### 2015-12-31 paper.tex
Acknowledge bob's feedback & help

The first author wishes to thank Robert Harper for numerous conversations about
abstract binding trees and symbolic parameters, and Andy Pitts for his help in
understanding multi-sorted nominal sets and atomic sheaves.

>>>>

The first author wishes to thank Robert Harper for numerous conversations about
abstract binding trees and symbolic parameters, and for his feedback on a draft
of this paper; and Andy Pitts for his help in understanding multi-sorted
nominal sets and atomic sheaves.
